\section{Data Used within the Project} \label{DataDefined}
Apart from research purposes, there has been little data used within this
project.  The StiCo algorithm pseudo code was taken from the 'Stigmergic
Coverage Algorithm for Multi-Robot Systems (Demonstration)' paper
\cite{Ranjbar-Sahraei2012Demo}.  For the introductory stages (Designing the
solution, defining the Project Requirements), this was the only information
used in a fashion outside of citation or referencing.

During the implementation stage, I have been looking through the available
sample code which was obtained from the 'GCtronic Wikipedia website'
\cite{gCtronicEpuckSite} as a base of understanding when it came to coding
the StiCo Algorithm.  I have also simulated some tests whilst I was
building the source code for the e-Puck robots.

Tangentially related data throughout the project includes documentation on the
various pieces of software I have used throughout this project.  An incomplete
list would include the text editors and IDEs that I have used (Vim, MPLAB X,
TeXstudio) as well as the simulation programs for the e-puck Robot (ENKI,
v-Rep).

\section{Ethical use of Data} \label{DataEthics}
To the author's knowledge, only synthetic data has been used within this
project, which is the information created by the author, for the sole purpose
being this project.  Whilst source code has been examined during this project
with the purpose of understanding coding concepts that are unfamiliar, along
with previously made header files as part of controlling the robot (in terms of
firmware), nothing has been knowingly taken without required authorisation.
The firmware used is currently included within the project's repository 
\cite{GithubRepo} for the sake of completeness and compatibility.
There has been no data which has been used within this project that is outside
of what has been defined within this chapter.

\section{Ethical use of Participants} \label{DataParticipants}
There have been no official participants within this project.  Whilst the
author has unofficially discussed potential options in completing this project
with colleagues and superiors during times of leisure, for the sake of
obtaining their opinion in the author's progress, there have been no
collaborators in designing, building or testing for the project.