\section{Maintaining competence}
I find maintaining competence over a field that has been previously learnt to
be an important factor - especially within the realm of IT and Computer
Science.  As robotics is a budding field within Computer Science, there is
much to be learnt by creating agents to perform autonomous tasks and it is
important to follow any developments closely should a time or vocation require
me to put my hands to Robotics and Artificial Intelligence again.

\section{Use Appropriate Methods and Tools}
Whilst I used the appropriate tools within this project - building the
workspace with a specialised IDE, constructing the source code in a favoured
editor and simulating in a specialised environment - my methods in doing so
were flawed.  This would be due to a potential lack of knowledge in using IDEs
and not finalising the set up of the workspace until coding was complete.  This
became a mistake and not something that will be repeated in the future.

\section{Managing Workload}
This is a tricky section of the British Computer Society's (BCS's) Code of
Practice \cite{codeOfPractice} for myself as I have little experience in
personal projects which have deadlines, and can therefore not qualify in
defining what an acceptable weight of workload is yet.  Communication was not a
strong point in this project due to personal restrictions which are being
worked upon and improved constantly.

\section{Tracking Progress within a Project}
I have used 'GitHub' as my method of storing my project \cite{GithubRepo}, as I
enjoy the portability granted to me and the ease of use it has given me whilst
interacting with this project.  What could have been utilised more is the
statistics available to me as a part of using GitHub, or having more than one
way to track progress, instead of simply a Gantt chart.

\section{Professional Competence and Integrity}
This project has been a big part of my professional development - it has been a
continuing source of progress, learning and understanding in relation to how I
carry out my work and the dangers that some habits can have when you are not
flexible enough for a project.  Informal advice from other students have been
useful in helping me to ground the concepts that have been formed and shown
within this document.  To my knowledge, all legislation has been followed
correctly where applicable.