A major learning point to be taken from this project would be the importance of
knowing enough of the basic principles within a project before deciding to
partake in it.  Whilst I have enjoyed myself and have learned much from the
work and studying that has gone into this project, I believe that it would have
been better if I had more familiarity with what was asked of me so that there
would have been a faster pace throughout the project.

Time Management.  This is an important area for me, as it is something that
I've always been able to do well, but sporadically.  As a fairly organised
person mentally and in my thought processes, this sometimes does not transfer
to paper, as it were - I have trouble in keeping on top of the deadlines that
I have no control over.  This project has instilled some discipline and,
personal distractions aside, it is something I will continue to work towards
as it becomes an ever more required trait within my professional life.

Focus has been something of a blessing and a curse within this project.  I am
capable of sitting down and completing something in a single 'session' as it
is my preference in case I come back to my work later and it is not commented
enough or I forget my trail of thought for the document.  This also causes me
to wait until later in the project with a false sense of available time.  I am
not averse to working, just the notion of starting work - similar to how a
writer may become blocked from staring at blank paper thinking of an article.
This is something I will improve upon by having a personal project on the side,
as a positive hobby to distract myself with fully.

Being familiar with the tools before work begins.  I enjoy working on the job
and improving my skills through practical exercises but this was not the
approach to take for this project.  What was required was a methodical stance
which catered towards slowly building up the deliverables after spending time
on truly understanding the workspace.  I will spend more of my time reading the
documentation and getting used to the interface of a program I am using as part
of a project, so I can get used to it before being required to run and interact
with the program.
