%What criteria to evaluate system?
\subsection{Evaluation Criteria} \label{desEvalCrit}
As mentioned earlier in the document[\ref{desSysEval}], the elements that fall
under evaluation are the dark room to be constructed and the compiled program
that will be placed on the e-Puck robotic system to demonstrate the 
effectiveness of the construct as a dark room.

\begin{description}
  \item[The Dark Room] \hfill \\
  \begin{itemize}
    \item The room can contain multiple robots
    \item Light level is low enough to not affect the glow in the dark flooring
    \item Being able to view the robots without leaking light into the arena
    \item Portable and flexible; easy to set up
  \end{itemize}
  \item[The Compiled Program] \hfill \\
  \begin{itemize}
    \item Helps to evaluate the dark room
    \item Interacts with the light messages left on the flooring
    \item Implements the StiCo algorithm
  \end{itemize}
\end{description}

%user friendliness
%users' feedback, etc.
It is difficult to evaluate how user friendly the final products will be.  This
is because the user will have minimal interaction with the robots.  The robots
will flash to indicate a change in the algorithm that will be executed.  To
construct the dark room, the user will require basic knowledge of creating
knots.  There are no users to acquire feedback from.

%How to assess these criteria?
The criteria will be mainly assessed when the dark room is completed.  Robots
can be placed within the arena to assess the correct size.  A handheld torch
will be used to test whether the flooring can hold a charge, and to see the
difference between ambient charge and directly exciting the flooring.
Evaluating the robot's capabilities can be done using only one agent, by using
a torch to simulate another agent's light trail and seeing a change in
agent's behaviour.

%Who are involved in evaluation?
Evaluation will be primarily completed by one person, as there are only one
person required to set up the robots and their states.  

%Ethical use of Human Data & Human Participants, if any.
There is no use of Human Data or Human Participants within this project -- all
parts of the project are covered by one person and therefore does not require
ethical limitations to be placed upon the project.

%What conclusion expected?
The conclusion of the project is expected to be a small arena to be used to
simulate darkness or night time situations.  The robot will be expected to
interact with light trails on the flooring in the manner that StiCo defines.
