%Modified Gantt chart
%\subsection{Gantt Chart}
\begin{ganttchart}[y unit chart=0.9cm]{24}{24}
\gantttitle{2015}{12} \gantttitle{2016}{12} \\
\gantttitlelist{1,...,12}{1} \gantttitlelist{1,...,12}{1} \\
\ganttgroup{Req.}{1}{4} \\
\ganttbar[name=reqRes]{Research}{1}{3} \\
\ganttbar[name=reqWrite]{Req. Write Up}{4}{4} \\
\ganttlink{reqRes}{reqWrite}

\ganttgroup{Des.}{5}{8} \\
\ganttbar[name=desArena]{ArenaBlueprints}{5}{7} \\
\ganttbar[name=desAlSearch]{AlgorithmResearch}{5}{6} \\
\ganttbar[name=desPseudo]{PseudoCode}{7}{7} \\
\ganttmilestone[name=milDesFin]{Des. Content Finished}{7} \\
\ganttbar[name=desWrite]{Des. Write Up}{8}{8} \\
\ganttlink{desArena}{milDesFin}
\ganttlink{desAlSearch}{desPseudo}
\ganttlink{desPseudo}{milDesFin}
\ganttlink{milDesFin}{desWrite}

\ganttgroup{Imp.}{9}{20} \\
\ganttbar[name=impArena]{Build Arena}{9}{11} \\
\ganttbar[name=impFamiliar]{Coding Robot famil.}{10}{11} \\
\ganttmilestone[name=milArenaFin]{Built Dark Room}{11} \\
\ganttbar[name=impBasicCode]{Basic Code}{12}{14} \\
\ganttbar[name=impAdvCode]{Advanced Code}{15}{17} \\
\ganttmilestone[name=milCodeFin]{Finished Coding}{17} \\
\ganttbar[name=impRefactor]{Refactor}{18}{18} \\
\ganttbar[name=impWrite]{Imp. Write Up}{19}{20} \\
\ganttlink{impArena}{milArenaFin}
\ganttlink{impFamiliar}{milArenaFin}
\ganttlink{milArenaFin}{impBasicCode}
\ganttlink{impBasicCode}{impAdvCode}
\ganttlink{impAdvCode}{milCodeFin}
\ganttlink{milCodeFin}{impRefactor}
\ganttlink{milCodeFin}{impWrite}
\end{ganttchart}
\clearpage

%Progress to date
\subsection{Current Progress}
The project is currently going slightly ahead of schedule.  I am 
reading on how to implement a coding solution for the e-Puck robotic system and
looking for materials to make the posts used to hold up the Cover for the dark 
room.  

%necessary changes in the project up to this point
\subsection{Changes within the project}
The algorithm which will be implemented is now defined as the StiCo algorithm.
If there are more unforeseeable changes, such as having to change the dimensions
of the arena, the proposed solution should be adequately adaptable.  